---
title: "p8105 Homework Assignment 1"
author: "Dionna Attinson"
date: "9/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
library(tidyverse)
```

# Problem 1 
```{R Question_1}
la_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("D", "N", "A", "T","T","I","N","S"),
  vec_factor = factor(c("BLACK", "BLACK", "BLACK", "WHITE", "WHITE", "WHITE","OTHER","OTHER"))
)
mean(pull(la_df, norm_samp))
mean(pull(la_df, norm_samp_pos))
mean(pull(la_df, vec_char))
mean(pull(la_df, vec_factor))
```
### The mean for variables norm_samp and norm_samp_pos have the ability to be calculated. However, the mean for vector characters and vector factors are unable to be calculated. 
```{r Question_1A, results="hide"}
  mean(as.numeric(pull(la_df,norm_samp_pos)))
  mean(as.numeric(pull(la_df,vec_char)))
  mean(as.numeric(pull(la_df,vec_factor)))
```
### When applying the as.numeric function to the logical, character, and factor variables, the mean was able to be calculated for the logical and factor variables but not the character variables.
```{r Question_1B}
  pull(la_df,norm_samp)*(as.numeric(pull(la_df,norm_samp_pos)))
  pull(la_df,norm_samp)*(as.factor(pull(la_df,norm_samp_pos)))
  pull(la_df,norm_samp)*(as.numeric(as.factor(pull(la_df,norm_samp_pos))))
```
# Problem 2 
```{r}
set.seed(1234)

plot_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  log_vec = x + y > 1 ,
)
  as.numeric(pull(plot_df, log_vec))
  as.factor(pull(plot_df, log_vec))
  
  nrow(plot_df)
  ncol(plot_df)
  
  mean((pull(plot_df,x)))
  median((pull(plot_df,x)))
  sd((pull(plot_df,x)))
```

The table `plot_df` has `nrow(plot_df)` rows and `ncol(plot_df)` columns. The mean, median, and standard deviation of variable `x` is `mean((pull(plot_df,x)))` median((pull(plot_df,x))),` and `sd((pull(plot_df,x)))`
```